Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2018-03-30 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Update macro a little bit...

% https://tex.stackexchange.com/questions/303018/minipage-reset-indent-how-can-i-set-again-to-standard
\edef\docIndent{\the\parindent}
\edef\docParskip{\the\parskip}
\newenvironment{docParinfo}{%
 \edef\currentIndent{\the\parindent}
 \edef\currentParskip{\the\parskip}
 \setlength{\parindent}{\docIndent}%
 \setlength{\parskip}{\docParskip}
}{
 \setlength{\parindent}{\currentIndent}%
 \setlength{\parskip}{\currentParskip}
}
\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\amr}[1]{\says{green}{Amr}{#1}}
\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
\newcommand{\gerardo}[1]{\says{OliveGreen}{Gerardo}{#1}}
\newcommand{\andy}[1]{\says{blue}{Andy}{#1}}
% \excludecomment{suggest}
\NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}
\newenvironment{compare}{\begin{widetext}\end{widetext}}{\begin{widetext}\end{widetext}}
\newenvironment{compareNextpage}{\clearpage}{\begin{widetext}\end{widetext}}
\NewDocumentEnvironment{compareText}{m m}{\noindent\begin{minipage}[b]{1\columnwidth}#1{The following is #2 text.}\begin{docParinfo}}{\end{docParinfo}#1{The #2 text end here.}\end{minipage}}
\newenvironment{oldText}[1]{\begin{compareText}{#1}{old}}{\end{compareText}\penalty-10000}
\newenvironment{newText}[1]{\begin{compareText}{#1}{new}}{\end{compareText}}

>>>>

% https://tex.stackexchange.com/questions/303018/minipage-reset-indent-how-can-i-set-again-to-standard
\edef\docIndent{\the\parindent}
\edef\docParskip{\the\parskip}
\newenvironment{docParinfo}{%
 \edef\currentIndent{\the\parindent}
 \edef\currentParskip{\the\parskip}
 \setlength{\parindent}{\docIndent}%
 \setlength{\parskip}{\docParskip}
}{
 \setlength{\parindent}{\currentIndent}%
 \setlength{\parskip}{\currentParskip}
}
\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\amr}[1]{\says{green}{Amr}{#1}}
\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
\newcommand{\gerardo}[1]{\says{OliveGreen}{Gerardo}{#1}}
\newcommand{\andy}[1]{\says{blue}{Andy}{#1}}
% \excludecomment{suggest}
\NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}
\NewDocumentEnvironment{compare}{m}{\begin{widetext}#1{The following left column should be replaced by the right column.}\end{widetext}}{\begin{widetext}#1{End of replacement.}\end{widetext}}
\newenvironment{compareText}{\noindent\begin{minipage}[b]{1\columnwidth}\begin{docParinfo}}{\end{docParinfo}\end{minipage}}
\newenvironment{oldText}{\begin{compareText}}{\end{compareText}\penalty-10000}
\newenvironment{newText}{\begin{compareText}}{\end{compareText}}
